\section{Discussion}
%One of the main objectives of this study was to design a navigational method in which an interplay between the physical and virtual world occurs. We proposed a navigational method that incorporated location-based game activities, where participants navigated by solving riddles in the virtual space about landmarks in the physical space. 
Results from our study clearly indicates that landmark navigation in combination with game activities between POIs is a more fun way of navigating than a 2D digital map. However, findings from interviews with the families revealed that children in particular also enjoyed navigating with maps. Children were challenged using the map as well as riddles for navigation, perhaps because they are not used to any of the navigational methods. We found that children thought they were better at navigating with riddles than maps. Similarly, parents were significantly more in flow with riddle-based navigation than with the 2D map, meaning there was a better challenge-skill balance with riddle-based navigation. One of the explanations could be that parents were less challenged by using maps, as they are used to navigate with maps, while riddle-based navigation was just as novel an experience for the parents as for the children. Particularly in the beginning, we observed that our test participants experienced difficulties understanding the rules of the riddle-based navigation, e.g. how long to walk before finding the answer to the riddle, which was supported by the fact that participants spent most time on the first riddle. Questionnaire data also  supported this, as riddles scored lower on clear goals. We assume that maps were less challenging to use, despite of the GPS problems that occured during the experiment, and therefore that challenge was one of the main reasons why riddle-based navigation scored higher on enjoyment. 

We found no significant results about presence, though riddle-based navigation scored higher on making the participants aware of their surroundings. One of the main objectives of this study was to create a navigational method with a stronger interplay between the physical and virtual space. Interview data revealed different opinions on whether participants were more or less aware of the surroundings using riddle-based navigation, where landmarks are used to navigate between POIs. With map navigation, some participants felt that they were more free to notice things in the surroundings, while riddle-based navigation only made some more aware of the landmarks. Others emphasized that one of the qualities of riddle-based navigation was that it made one aware of things that otherwise would have gone unnoticed.

Despite not being the main focus of this study, our most prevailing findings were in terms of social interaction among participants. Even though we did not find any statistically significant results supporting that participants helped each other more during riddle-based navigation, compared to a map, we found that riddle-based navigation has potentials in motivating groups of people, making it a enjoyable group experience rather just a matter of getting from A to B, where on person is in charge. We observed that participants discussed more and that topics revolved around solving the riddles, discussing the landmarks and not on topics outside the activity, as it was the case with map navigation. Though this requires a more thorough analysis of the interaction among the participants, we conclude that riddle-based navigation has potentials in supporting learning as seen previously with \textit{CityTreasure} (kilde), where knowledge of the physical space is incorporated in engaging the players. Even though enjoyment is the main objective of most LBGs as mentioned by Avouris \& Yiannoutsou, we recommend looking into riddle-based navigation or similar approaches for informal learning. 



%However, we found no statistically significant results in terms of participants helping each other more during riddle-based navigation. 

%- Social interaction --> Potential in motivating groups of people, making it a family experience rather than a matter of getting from A to B. Potentials in terms of learning about the environment. 